\chapter*{Abstract}
The need for better battery materials is driven by the move towards electric vehicles and the intermittent renewable energy sources.
With current technologies at their technical limits, and a strong need to decouple energy storage from the availability of endangered element supplies, the development of novel battery materials is urgently needed.
An understanding of the fundamental mechanisms and phenomena which underpin the performance of these materials can identify new candidates and aid in the improvement and commercialisation of known materials.

Computational techniques can offer insights into the energetics of defect formation and ion mobility in battery materials, providing an understanding not obtainable by experimental studies alone.

Energy minimisation and molecular dynamics techniques have been applied to a disordered rock-salt, \ce{Li4Mn2O5}, in order to characterise its performance as a cathode material.
The disordered nature of this system raise a number of issues which hinder the use of conventional computational methods alone.
A need for structure generation techniques which account for the energetics of local environments has been identified, as purely random assignment of ions to lattice sites leads to the formation of unphysical states.

The study of an ordered analogue of \ce{Li4Mn2O5} provided insight into energetics of defect formation, showing low concentrations of Schottky and Frenkel defects are to be expected.
The ordered nature of the structure gave rise to a difference in lithium vacancy formation energies, which in turn led to unfavourable and highly anisotropic migration pathways.

